\begin{thebibliography}{9}
\bibitem{abs1}
"What is Colossus?," www.computerhope.com. https://www.computerhope.com/jargon/c/colossus.htm

\bibitem{abs2}
Wikipedia Contributors, "Dot-com bubble," Wikipedia, Mar. 21, 2019. https://en.wikipedia.org/wiki/Dot-com\_bubble

\bibitem{abs3}
Booking.com, "Booking.com: The largest selection of hotels, homes, and vacation rentals," Booking.com, 2019. https://www.booking.com/

\bibitem{abs4}
eBay, "Electronics, Cars, Fashion, Collectibles, Coupons and More | eBay," eBay, 2019. https://www.ebay.com/

\bibitem{abs5}
Figma, "Figma: the collaborative interface design tool.," Figma, 2019. https://www.figma.com/

\bibitem{abs6}
"Roadmap - WebAssembly," webassembly.org. https://webassembly.org/roadmap/

\bibitem{abs7}
"Made with WebAssembly," madewithwebassembly.com. https://madewithwebassembly.com/

\bibitem{abs8}
"Figma is powered by WebAssembly," Figma, Jun. 08, 2017. https://www.figma.com/blog/webassembly-cut-figmas-load-time-by-3x/

\bibitem{abs9}
J. Kastrenakes, "Adobe brings a simplified Photoshop to the web," The Verge, Oct. 26, 2021. https://www.theverge.com/2021/10/26/22738125/adobe-photoshop-illustrator-web-announced (accessed Nov. 05, 2022).

\bibitem{abs10}
P. Clark, "Photoshop ships major updates across desktop and iPad apps; Extends Light Editing and Collaboration features to the web (beta)|Adobe," Adobe Blog. https://blog.adobe.com/en/publish/2021/10/26/photoshop-ships-major-updates-across-desktop-ipad-apps-extends-light-editing-collaboration-features-web-beta (accessed Nov. 05, 2022).

\bibitem{abs11}
"Photoshop’s journey to the web," web.dev. https://web.dev/ps-on-the-web/ (accessed Nov. 05, 2022).

\bibitem{abs12}
B. Spies and M. Mock, "An Evaluation of WebAssembly in Non-Web Environments," 2021 XLVII Latin American Computing Conference (CLEI), 2021, pp. 1-10, doi: 10.1109/CLEI53233.2021.9640153.

\bibitem{abs13}
A. Jangda, B. Powers, E. Berger, and A. Guha, “Not so fast: Analyzing the performance of WebAssembly vs. Native code,” arXiv [cs.PL], 2019.

\bibitem{int1}
"WWDC 2017 — APPOCALYPSE — Apple," www.youtube.com. https://www.youtube.com/watch?v=mPnl1aazs98

\bibitem{int2}
Google, "Google Scholar," Google.com.au, 2019. https://scholar.google.com.au/

\bibitem{int3}
"The New England Journal of Medicine: Research \& Review Articles on Disease \& Clinical Practice," New England Journal of Medicine, 2000. https://www.nejm.org/

\bibitem{int4}
J. Bergdahl, "JS is weird," jacobbergdahl.com. https://jsisweird.com/ (accessed Nov. 05, 2022).

\bibitem{int5}
"Documentation - TypeScript for the New Programmer," www.typescriptlang.org. https://www.typescriptlang.org/docs/handbook/typescript-from-scratch.html

\bibitem{int6}
"Why You Should Use React.js For Web Development," freeCodeCamp.org, Feb. 18, 2021. https://www.freecodecamp.org/news/why-use-react-for-web-development (accessed Nov. 05, 2022).

\bibitem{int7}
"Inventing the Internet," www.youtube.com. https://www.youtube.com/watch?v=BnFJ8cHAlco (accessed Nov. 05, 2022).

\bibitem{int8}
A. Gore, "S.272 - 102nd Congress (1991-1992): High-Performance Computing Act of 1991," www.congress.gov, Dec. 09, 1991. https://www.congress.gov/bill/102nd-congress/senate-bill/272

\bibitem{int9}
"NCSA Mosaic -- September 10, 1993 Demo," totic.org. http://totic.org/nscp/demodoc/demo.html (accessed Nov. 05, 2022).

\bibitem{int10}
T. B. Lee, "The internet, explained," Vox, Jun. 16, 2014. https://www.vox.com/2014/6/16/18076282/the-internet

\bibitem{int11}
"A Brief History of JavaScript," DEV Community. https://dev.to/dboatengx/history-of-javascript-how-it-all-began-92a

\bibitem{int12}
Oracle.com, 2022. https://developer.oracle.com/javascript/what-is-javascript/ (accessed Nov. 05, 2022).

\bibitem{int13}
"Microsoft Launches Microsoft Internet Explorer 3.0 With Exclusive, Free Content Offers From Top Web Sites," Stories, Aug. 13, 1996. https://news.microsoft.com/1996/08/13/microsoft-launches-microsoft-internet-explorer-3-0-with-exclusive-free-content-offers-from-top-web-sites/

\bibitem{int14}
"Goodbye, Flash: The web application everybody used — and hated," NBC News, Dec. 31, 2020. Accessed: Jan. 02, 2021. [Online]. Available: https://www.nbcnews.com/tech/internet/goodbye-flash-web-application-everybody-used-hated-n1252607

\bibitem{int15}
"Infographic: The End of the Flash Era," Statista Infographics. https://www.statista.com/chart/3796/websites-using-flash/

\bibitem{int16}
"Adobe Flash Player Enterprise End of Life," www.adobe.com. https://www.adobe.com/products/flashplayer/enterprise-end-of-life.html

\bibitem{inta1}
https://devhumor.com/media/javascript-is-weird

\bibitem{int17}
"WebAssembly," webassembly.org. https://webassembly.org/

\bibitem{int18}
A. Haas et al., "Bringing the web up to speed with WebAssembly", ACM SIGPLAN Notices, vol. 52, no. 6, pp. 185-200, 2017. Available: 10.1145/3140587.3062363.

\bibitem{int19}
A. Jangda, B. Powers, E. Berger, and A. Guha, “Not so fast: Analyzing the performance of WebAssembly vs. Native code,” arXiv [cs.PL], 2019.

\bibitem{int20}
"Polyglot (computing)," Wikipedia, Sep. 23, 2022. https://en.wikipedia.org/wiki/Polyglot\_(computing) (accessed Nov. 05, 2022).

\bibitem{int21}
".NET | Free. Cross-platform. Open Source.," Microsoft. https://dotnet.microsoft.com/en-us/

\bibitem{int22}
Wikipedia Contributors, ".NET Framework," Wikipedia, Apr. 29, 2019. https://en.wikipedia.org/wiki/.NET\_Framework

\bibitem{int23}
Wikipedia Contributors, "Visual Basic .NET," Wikipedia, Apr. 14, 2019. https://en.wikipedia.org/wiki/Visual\_Basic\_.NET

\bibitem{int24}
BillWagner, "C\# docs - get started, tutorials, reference.," learn.microsoft.com. https://learn.microsoft.com/en-us/dotnet/csharp/

\bibitem{int25}
"How to mix C\# and VB.net in the same project," www.cryer.co.uk. https://www.cryer.co.uk/brian/mswinswdev/ms\_dotnet\_mix\_csharp\_and\_vb.htm (accessed Nov. 05, 2022).

\bibitem{int26}
M. Georgescu and D. Milodin, "Open Source Tools to Assist in the Development of Software Applications, " Open Source Science Journal, 2010, Vol. 2, No. 2.

\bibitem{int27}
Node.js Foundation, "Node.js," Node.js, 2019. https://nodejs.org/en/

\bibitem{int28}
Slack, "Where Work Happens," Slack, 2018. https://slack.com/

\bibitem{int29}
Zoom, "Video conferencing, web conferencing, webinars, screen sharing," Zoom Video, 2022. https://zoom.us/

\bibitem{int30}
WhatsApp, "WhatsApp," WhatsApp.com, 2018. https://www.whatsapp.com/

\bibitem{int31}
"V8 JavaScript engine," v8.dev. https://v8.dev/

\bibitem{int32}
adegeo, "Windows Presentation Foundation for .NET 5 documentation," learn.microsoft.com. https://learn.microsoft.com/en-us/dotnet/desktop/wpf/?view=netdesktop-6.0

\bibitem{int33}
QuinnRadich, "UWP Documentation - UWP app developer," learn.microsoft.com. https://learn.microsoft.com/en-us/windows/uwp/ (accessed Nov. 06, 2022).

\bibitem{int34}
"Swing (Java)," Wikipedia, Nov. 17, 2019. https://en.wikipedia.org/wiki/Swing\_(Java)

\bibitem{int35}
deepu, "Visualizing memory management in V8 Engine (JavaScript, NodeJS, Deno, WebAssembly)," Technorage, Jan. 27, 2020. https://deepu.tech/memory-management-in-v8/ (accessed Nov. 06, 2022).

\bibitem{int36}
T. Warren, "Chrome now uses more RAM because of Spectre security fixes," The Verge, Jul. 12, 2018. https://www.theverge.com/2018/7/12/17564064/google-chrome-ram-usage-memory-increase-spectre-fixes (accessed Nov. 06, 2022).

\bibitem{int37}
"Safari," Apple, 2018. https://www.apple.com/safari/

\bibitem{int38}
"macOS Big Sur - Apple," web.archive.org, Oct. 18, 2021. https://web.archive.org/web/20211018064504/https://www.apple.com/macos/big-sur/ (accessed Nov. 06, 2022).

\bibitem{int39}
"Chrome Used 10X More RAM Than Safari on macOS Big Sur in Recent Test [Updated]," MacRumors. https://www.macrumors.com/2021/02/20/chrome-safari-ram-test/ (accessed Nov. 06, 2022).

\bibitem{int40}
"Exploring lighter alternatives to Electron for hosting a Blazor desktop app," Steve Sanderson’s Blog. https://blog.stevensanderson.com/2019/11/01/exploring-lighter-alternatives-to-electron-for-hosting-a-blazor-desktop-app/ (accessed Nov. 06, 2022).

\bibitem{lit1}
"Three Protocols, the | Encyclopedia.com", Encyclopedia.com, 2022. [Online]. Available: https://www.encyclopedia.com/economics/encyclopedias-almanacs-transcripts-and-maps/three- protocols. [Accessed: 02-May-2022].

\bibitem{lit2}
"Roadmap - WebAssembly", Webassembly.org, 2022. [Online]. Available: https://webassembly.org/roadmap/. [Accessed: 02-May-2022].

\bibitem{lit3}
Möller, Andreas \& Michahelles, Florian \& Diewald, Stefan \& Roalter, Luis \& Kranz, Matthias. (2012). Update Behavior in App Markets and Security Implications: A Case Study in Google Play.

\bibitem{lit4}
"App Store," Apple. https://www.apple.com/app-store/

\bibitem{lit5}
"Google Play," Google.com, 2009. https://play.google.com/

\bibitem{lit6}
"Turning Off Auto Updates in Google Chrome", Chromium.org, 2022. [Online]. Available: https://www.chromium.org/administrators/turning-off-auto-updates/. [Accessed: 02-May-2022].

\bibitem{lit7}
Apple Support. 2022. How to manually update apps on your Apple device. [online] Available at: <https://support.apple.com/HT202180> [Accessed 2 May 2022].

\bibitem{lit8}
D. Geer, "Auto-Update Considered Harmful" in IEEE Security \& Privacy, vol. 19, no. 02, pp. 79- 80, 2021. doi: 10.1109/MSEC.2021.3050248

\bibitem{lit9}
B. M. Luettmann and A. C. Bender, "Man-in-the-middle attacks on auto-updating software," in Bell Labs Technical Journal, vol. 12, no. 3, pp. 131-138, Fall 2007, doi: 10.1002/bltj.20255.

\bibitem{lit10}
Insane, Facebook.com. Apr. 2022. [online] Available at: <https://www.facebook.com/TheInsaneApp/posts/532542348235323> [Accessed 2 May 2022].

\bibitem{lit11}
Haas, A., Rossberg, A., Schuff, D., Titzer, B., Holman, M., Gohman, D., Wagner, L., Zakai, A. and Bastien, J., 2017. Bringing the web up to speed with WebAssembly. ACM SIGPLAN Notices, 52(6), pp.185-200.

\bibitem{lit12}
"Benchmark of WebAssembly runtimes - 2021 Q1 | Frank DENIS random thoughts.," 00f.net. https://00f.net/2021/02/22/webassembly-runtimes-benchmarks/ (accessed Oct. 02, 2022).

\bibitem{lit13}
Microsoft. 2022. Blazor | Build client web apps with C\# | .NET. [online] Available at: <https://dotnet.microsoft.com/en-us/apps/aspnet/web-apps/blazor> [Accessed 2 May 2022].

\bibitem{lit14}
Micha Reiser and Luc Bläser. 2017. Accelerate JavaScript applications by cross-compiling to WebAssembly. In Proceedings of the 9th ACM SIGPLAN International Workshop on Virtual Machines and Intermediate Languages (VMIL 2017). Association for Computing Machinery, New York, NY, USA, 10–17. https://doi.org/10.1145/3141871.3141873

\bibitem{lit15}
David Herman, Wagner Luke, and Alon Zakai. 2014. asm.js. (2014). https://goo.gl/sxWVss

\bibitem{lit16}
Yutian Yan, Tengfei Tu, Lijian Zhao, Yuchen Zhou, and Weihang Wang. 2021. Understanding the performance of webassembly applications. In Proceedings of the 21st ACM Internet Measurement Conference (IMC '21). Association for Computing Machinery, New York, NY, USA, 533–549. https://doi.org/10.1145/3487552.3487827

\bibitem{lit17}
BenchmarkingWebAssembly. 2022. Input Size. [online] Available at: <https://benchmarkingwasm.github.io/BenchmarkingWebAssembly/input\_size.html> [Accessed 2 May 2022].

\bibitem{lit18}
W3schools.com. 2022. JavaScript History. [online] Available at: <https://www.w3schools.com/js/js\_history.asp> [Accessed 2 May 2022].

\bibitem{lit19}
"History of WebAssembly (Chrome University 2019)," www.youtube.com. https://www.youtube.com/watch?v=6r0NKEQqkz0 (accessed Oct. 02, 2022).

\bibitem{lit20}
Jangda, A., Powers, B., Berger, E. D., \& Guha, A. (2019). Not So Fast: Analyzing the Performance of WebAssembly vs. Native Code. 2019 USENIX Annual Technical Conference (USENIX ATC 19), 107–120. https://www.usenix.org/conference/atc19/presentation/jangda

\bibitem{lit21}
Browsix.org. 2022. Browsix: Unix in the browser tab. [online] Available at: <https://browsix.org/> [Accessed 2 May 2022].

\bibitem{lit22}
Node.js. 2022. Node.js. [online] Available at: <https://nodejs.org/> [Accessed 2 May 2022].

\bibitem{lit23}
GitHub. 2022. GitHub - gwsystems/aWsm: WebAssembly ahead-of-time compiler and runtime. Focuses on generating fast code, simplicity, and portability.. [online] Available at: <https://github.com/gwsystems/aWsm> [Accessed 2 May 2022].

\bibitem{lit24}
Wasmer.io. 2022. Wasmer - The Universal WebAssembly Runtime. [online] Available at: <https://wasmer.io/> [Accessed 2 May 2022].

\bibitem{lit25}
E. Wen and G. Weber, "Wasmachine: Bring IoT up to Speed with A WebAssembly OS," 2020 IEEE International Conference on Pervasive Computing and Communications Workshops (PerCom Workshops), 2020, pp. 1-4, doi: 10.1109/PerComWorkshops48775.2020.9156135.

\bibitem{lit26}
E. Wen and G. Weber, "Wasmachine: Bring the Edge up to Speed with A WebAssembly OS," 2020 IEEE 13th International Conference on Cloud Computing (CLOUD), 2020, pp. 353-360, doi: 10.1109/CLOUD49709.2020.00056.

\bibitem{lit27}
F. Eriksson and S. Grunditz, ‘Containerizing WebAssembly : Considering WebAssembly Containers on IoT Devices as Edge Solution’, Dissertation, 2021.

\bibitem{lit28}
Docker, "Enterprise Application Container Platform | Docker," Docker, 2018. https://www.docker.com/

\bibitem{lit29}
J. Napieralla, “Considering WebAssembly Containers for Edge Computing on Hardware-Constrained IoT Devices”, 2020.

\bibitem{lit30}
Amazon Web Services, Inc. 2022. Serverless Computing - AWS Lambda - Amazon Web Services. [online] Available at: <https://aws.amazon.com/lambda/> [Accessed 2 May 2022].

\bibitem{lit31}
Eismann, S., Scheuner, J., van Eyk, E., Schwinger, M., Grohmann, J., Herbst, N., Abad, C. L., \& Iosup, A. (2021). Serverless Applications: Why, When, and How? IEEE Software, 38(1), 32–39. https://doi.org/10.1109/ms.2020.3023302

\bibitem{lit32}
Gackstatter, P. (2021). A WebAssembly Container Runtime for Serverless Edge Computing (Doctoral dissertation, Wien). https://doi.org/10.34726/hss.2021.85181

\bibitem{lit33}
P. K. Gadepalli, G. Peach, L. Cherkasova, R. Aitken and G. Parmer, "Challenges and Opportunities for Efficient Serverless Computing at the Edge," 2019 38th Symposium on Reliable Distributed Systems (SRDS), 2019, pp. 261-2615, doi: 10.1109/SRDS47363.2019.00036.

\bibitem{lit34}
Phani Kishore Gadepalli, Sean McBride, Gregor Peach, Ludmila Cherkasova, and Gabriel Parmer. 2020. Sledge: a Serverless-first, Light-weight Wasm Runtime for the Edge. In Proceedings of the 21st International Middleware Conference (Middleware '20). Association for Computing Machinery, New York, NY, USA, 265–279. https://doi.org/10.1145/3423211.3425680

\bibitem{lit35}
"Nuclio", nuclio, 2022. [Online]. Available: https://nuclio.io/. [Accessed: 02- May- 2022].

\bibitem{lit36}
Kubernetes, "Production-Grade Container Orchestration," Kubernetes.io, 2019. https://kubernetes.io/

\bibitem{lit37}
M. Nieke, L. Almstedt, and R. Kapitza, "Edgedancer," Proceedings of the 4th International Workshop on Edge Systems, Analytics and Networking, Apr. 2021, doi: 10.1145/3434770.3459731.

\bibitem{lit38}
I. Pelle, J. Czentye, J. Dóka, A. Kern, B. P. Gerő and B. Sonkoly, "Operating Latency Sensitive Applications on Public Serverless Edge Cloud Platforms," in IEEE Internet of Things Journal, vol. 8, no. 10, pp. 7954-7972, 15 May15, 2021, doi: 10.1109/JIOT.2020.3042428.

\bibitem{lit39}
OpenCV, "OpenCV library," Opencv.org, 2019. https://opencv.org/

\bibitem{lit40}
"AWS IoT Greengrass - Amazon Web Services," Amazon Web Services, Inc., 2019. https://aws.amazon.com/greengrass/

\bibitem{lit41}
M. Xu et al., "From cloud to edge: a first look at public edge platforms," Proceedings of the 21st ACM Internet Measurement Conference, Nov. 2021, doi: 10.1145/3487552.3487815.

\bibitem{lit42}
"Extending the Boundaries of the Cloud with Edge Computing," Alibaba Cloud Community. https://www.alibabacloud.com/blog/extending-the-boundaries-of-the-cloud-with-edge-computing\_594214 (accessed Oct. 02, 2022).

\bibitem{lit43}
P. Gackstatter, P. A. Frangoudis and S. Dustdar, "Pushing Serverless to the Edge with WebAssembly Runtimes," 2022 22nd IEEE International Symposium on Cluster, Cloud and Internet Computing (CCGrid), 2022, pp. 140-149, doi: 10.1109/CCGrid54584.2022.00023.

\bibitem{lit44}
"Cloud Functions," Google Cloud. https://cloud.google.com/functions

\bibitem{lit45}
Apache OpenWhisk is a serverless, open source cloud platform," openwhisk.apache.org. https://openwhisk.apache.org/

\bibitem{eva1}
Amazon, "Amazon Web Services (AWS) - Cloud Computing Services," Amazon Web Services, Inc., 2022. https://aws.amazon.com/

\bibitem{eva2}
Google, "Cloud Computing Services  |  Google Cloud," Google Cloud, 2019. https://cloud.google.com/

\bibitem{eva3}
"Cloud Computing Services | Microsoft Azure," azure.microsoft.com. https://azure.microsoft.com

\bibitem{eva4}
"The Best Python Web Frameworks 2022," DEV Community. https://dev.to/theme\_selection/the-best-python-web-frameworks-d2d

\bibitem{exp1}
"Google Trends," Google Trends. https://trends.google.com/trends/explore?date=today\%205-y\&q=Edge\%20Computing (accessed Nov. 06, 2022).

\bibitem{exp2}
"Cloud Functions for Firebase," Firebase. https://firebase.google.com/docs/functions

\bibitem{exp3}
Cloudflare, "Cloudflare Workers, " Cloudflare.com, 2019. https://workers.cloudflare.com/ (accessed Dec. 30, 2019).

\bibitem{exp4}
"Next.js by Vercel - The React Framework," nextjs.org. https://nextjs.org/

\bibitem{exp5}
"Edge Network," Vercel Documentation. https://vercel.com/docs/concepts/edge-network/overview (accessed Nov. 06, 2022).

\bibitem{exp6}
Phani Kishore Gadepalli, Sean McBride, Gregor Peach, Ludmila Cherkasova, and Gabriel Parmer. 2020. Sledge: a Serverless-first, Light-weight Wasm Runtime for the Edge. In Proceedings of the 21st International Middleware Conference (Middleware '20). Association for Computing Machinery, New York, NY, USA, 265–279. https://doi.org/10.1145/3423211.3425680

\bibitem{exp7}
AWS, "AWS Lambda – Serverless Compute - Amazon Web Services," Amazon Web Services, Inc., 2019. https://aws.amazon.com/lambda/

\bibitem{exp8}
ggailey777, "Azure Functions documentation," docs.microsoft.com. https://docs.microsoft.com/en-us/azure/azure-functions/

\bibitem{exp9}
"Cloud Functions," Google Cloud. https://cloud.google.com/functions

\bibitem{exp10}
"Apache OpenWhisk is a serverless, open source cloud platform," openwhisk.apache.org. https://openwhisk.apache.org/

\bibitem{exp11}
Wikipedia Contributors, "Web framework," Wikipedia, Apr. 03, 2020. https://en.wikipedia.org/wiki/Web\_framework

\bibitem{exp12}
Wikipedia Contributors, "Web application," Wikipedia, Aug. 16, 2019. https://en.wikipedia.org/wiki/Web\_application

\bibitem{exp13}
Facebook, "React – A JavaScript library for building user interfaces," Reactjs.org, 2022. https://reactjs.org/

\bibitem{exp14}
Angular, "Angular," Angular.io, 2019. https://angular.io/

\bibitem{exp15}
E. You, "Vue.js," Vuejs.org, 2000. https://vuejs.org/

\bibitem{exp16}
Node.js Foundation, "Node.js," Node.js, 2019. https://nodejs.org/en/

\bibitem{exp17}
"ASP.NET | Open-source web framework for .NET," Microsoft. https://dotnet.microsoft.com/en-us/apps/aspnet

\bibitem{exp18}
Django, "The Web framework for perfectionists with deadlines | Django," Djangoproject.com, 2019. https://www.djangoproject.com/

\bibitem{exp19}
T. Christie, "Home - Django REST framework," Django-rest-framework.org, 2011. https://www.django-rest-framework.org/

\bibitem{exp20}
"Stack Overflow Developer Survey 2022," Stack Overflow. https://survey.stackoverflow.co/2022/

\bibitem{exp21}
Gackstatter, P. (2021). A WebAssembly container runtime for serverless edge computing [Diploma Thesis, Technische Universität Wien]. reposiTUm. https://doi.org/10.34726/hss.2021.85181

\bibitem{exp22}
Docker, "Enterprise Application Container Platform | Docker," Docker, 2018. https://www.docker.com/

\bibitem{exp23}
Kubernetes, "Production-Grade Container Orchestration," Kubernetes.io, 2019. https://kubernetes.io/

\bibitem{exp24}
"The Future of JavaScript," bnjbvr.github.io. https://bnjbvr.github.io/slides/2015/javascript-future-fosdem-2015 (accessed Nov. 06, 2022).

\bibitem{exp25}
"Google Chrome - The Fast, Simple and Secure Browser from Google," Google.com, 2017. https://www.google.com/chrome/

\bibitem{exp26}
"Secure, Fast \& Private Web Browser with Adblocker | Brave Browser," Brave Browser, 2018. https://brave.com/

\bibitem{exp27}
"V8 Benchmark Suite," www.netchain.com. https://www.netchain.com/Tools/v8/ (accessed Nov. 06, 2022).

\bibitem{exp28}
"Speedometer 1.0," browserbench.org. https://browserbench.org/Speedometer/ (accessed Nov. 06, 2022).

\bibitem{exp29}
"Celebrating 10 years of V8 · V8," v8.dev. https://v8.dev/blog/10-years (accessed Nov. 06, 2022).

\bibitem{exp30}
L. D. Pyeatt and W. Ughetta, ARM 64-bit assembly language. Kidlington, Oxford: Newnes, an imprint of Elsevier, 2020.

\bibitem{exp31}
"Bun is a fast all-in-one JavaScript runtime," bun.sh. https://bun.sh/ (accessed Nov. 06, 2022).

\bibitem{exp32}
"aWsm - An Awesome Wasm Compiler and Runtime," GitHub, Nov. 01, 2022. https://github.com/gwsystems/aWsm (accessed Nov. 06, 2022).

\bibitem{exp33}
"Rust Programming Language," Rust-lang.org, 2018. https://www.rust-lang.org/

\bibitem{exp34}
"Fermyon Gives Developers Instant Self-Service for WebAssembly Microservice Application Deployment With Fermyon Cloud, Closes \$20 Million Series A Funding Led by Insight Partners in Q3," au.finance.yahoo.com. https://au.finance.yahoo.com/news/fermyon-gives-developers-instant-self-133400963.html (accessed Nov. 06, 2022).

\bibitem{exp35}
J. Warren, "WebAssembly Pioneer Fermyon Raises \$20 Million Series A, Releases Fermyon Cloud," Forbes. https://www.forbes.com/sites/justinwarren/2022/10/24/webassembly-pioneer-fermyon-raises-20-million-series-a-releases-fermyon-cloud/?sh=240eb22f31bb (accessed Nov. 06, 2022).

\bibitem{exp36}
AWS, "Amazon EC2," Amazon Web Services, Inc., 2019. https://aws.amazon.com/ec2/

\bibitem{exp37}
"Server farm," Wikipedia, Nov. 01, 2022. https://en.wikipedia.org/wiki/Server\_farm (accessed Nov. 06, 2022).

\bibitem{exp38}
"Amazon EC2 Instance Types - Amazon Web Services," Amazon Web Services, Inc., 2019. https://aws.amazon.com/ec2/instance-types/

\bibitem{exp39}
"PolyBench/C -- Homepage of Louis-Noël Pouchet," web.cse.ohio-state.edu. https://web.cse.ohio-state.edu/~pouchet.2/software/polybench/ (accessed Nov. 06, 2022).

\bibitem{exp40}
"Home - Fortran Programming Language," fortran-lang.org. https://fortran-lang.org/

\bibitem{exp41}
M. Á. Abella-González, P. Carollo-Fernández, L.-N. Pouchet, F. Rastello, and G. Rodríguez, "PolyBench/Python: benchmarking Python environments with polyhedral optimizations," Proceedings of the 30th ACM SIGPLAN International Conference on Compiler Construction, Feb. 2021, doi: 10.1145/3446804.3446842.

\bibitem{exp42}
ORACLE, "Oracle VM VirtualBox," Virtualbox.org, 2019. https://www.virtualbox.org/

\bibitem{exp43}
Canonical, "The leading operating system for PCs, IoT devices, servers and the cloud | Ubuntu," Ubuntu, Jun. 19, 2019. https://ubuntu.com/

\bibitem{exp44}
"GCC, the GNU Compiler Collection - GNU Project - Free Software Foundation (FSF)," Gnu.org, 2019. https://gcc.gnu.org/

\bibitem{exp45}
"Clang C Language Family Frontend for LLVM," clang.llvm.org. https://clang.llvm.org/

\bibitem{exp46}
"Security - WebAssembly," webassembly.org. https://webassembly.org/docs/security/ (accessed Nov. 06, 2022).

\bibitem{exp47}
Wikipedia Contributors, "Bubble sort," Wikipedia, Oct. 21, 2019. https://en.wikipedia.org/wiki/Bubble\_sort

\bibitem{exp48}
Wikipedia Contributors, "Insertion sort," Wikipedia, Nov. 15, 2019. https://en.wikipedia.org/wiki/Insertion\_sort

\bibitem{exp49}
Wikipedia Contributors, "Quicksort," Wikipedia, Oct. 23, 2019. https://en.wikipedia.org/wiki/Quicksort

\bibitem{exp50}
"The Sound of Sorting - 'Audibilization' and Visualization of Sorting Algorithms - panthema.net," panthema.net. https://panthema.net/2013/sound-of-sorting/

\bibitem{exp51}
"15 Sorting Algorithms in 6 Minutes," YouTube. May 20, 2013. [YouTube Video]. Available: https://www.youtube.com/watch?v=kPRA0W1kECg

\bibitem{exp52}
T. Bingmann, "The Sound of Sorting - Visualization and ‘Audibilization’ of Sorting Algorithms," GitHub, Oct. 12, 2022. https://github.com/bingmann/sound-of-sorting (accessed Nov. 06, 2022).

\bibitem{exp53}
"Amazon ECR | Docker Container Registry | Amazon Web Services," Amazon Web Services, Inc. https://aws.amazon.com/ecr/

\bibitem{exp54}
"Amazon ECS - Run containerized applications in production," Amazon Web Services, Inc. https://aws.amazon.com/ecs/

\bibitem{exp55}
"Docker Hub," hub.docker.com. https://hub.docker.com/\_/ubuntu

\bibitem{exp56}
"Install Spin," Fermyon Developer, Mar. 14, 2022. https://developer.fermyon.com/spin/install (accessed Nov. 06, 2022).

\bibitem{exp57}
AWS, "Content Delivery Network (CDN) | Low Latency, High Transfer Speeds, Video Streaming | Amazon CloudFront," Amazon Web Services, Inc., 2018. https://aws.amazon.com/cloudfront/

\bibitem{exp58}
Wikipedia Contributors, "Dijkstra’s algorithm," Wikipedia, May 28, 2019. https://en.wikipedia.org/wiki/Dijkstra\%27s\_algorithm

\bibitem{exp59}
Wikipedia Contributors, "Floyd–Warshall algorithm," Wikipedia, May 16, 2019. https://en.wikipedia.org/wiki/Floyd\%E2\%80\%93Warshall\_algorithm

\bibitem{exp60}
Wikipedia Contributors, "Kruskal’s algorithm," Wikipedia, Oct. 08, 2019. https://en.wikipedia.org/wiki/Kruskal\%27s\_algorithm

\bibitem{exp61}
"Spanning Tree and Minimum Spanning Tree," www.programiz.com. https://www.programiz.com/dsa/spanning-tree-and-minimum-spanning-tree\#minimum-spanning (accessed Nov. 06, 2022).

\bibitem{expa1}
"Kruskal’s Algorithm," www.programiz.com. https://www.programiz.com/dsa/kruskal-algorithm

\bibitem{exp62}
"Prim’s Algorithm," www.programiz.com. https://www.programiz.com/dsa/prim-algorithm

\bibitem{exp63}
"Difference between Prim’s and Kruskal’s Algorithm for MST," BYJUS. https://byjus.com/gate/difference-between-prims-and-kruskal-algorithum/

\bibitem{res1}
"Bucket Sort Algorithm," www.programiz.com. https://www.programiz.com/dsa/bucket-sort
\end{thebibliography}